%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
% \usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{siunitx}
\usepackage{mathtools} %for delimiters
\usepackage{braket}
\usepackage{gensymb}
\usepackage{natbib}
\bibliographystyle{apalike}

% for bibliography compatibility
\DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
\DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
\DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
\DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
\DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
\DeclareOldFontCommand{\sl}{\normalfont\slshape}{\@nomath\sl}
\DeclareOldFontCommand{\sc}{\normalfont\scshape}{\@nomath\sc}
\DeclareRobustCommand*\cal{\@fontswitch\relax\mathcal}
\DeclareRobustCommand*\mit{\@fontswitch\relax\mathnormal}

\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
% Swap the definition of \abs* and \norm*, so that \abs
% and \norm resizes the size of the brackets, and the
% starred version does not.
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

\sisetup{
    %output-decimal-marker={,}% just uncomment if you want to use comma as the decimal marker!
}

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers

\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

% \setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{
\normalfont \normalsize
\textsc{The Open University} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge A Critical evaluation of Quantum Key Distribution, focusing on SARG04 as a benchmark \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{William Ockmore} % Your name

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

\tableofcontents

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction}

Quantum key distribution is the study of quantum mechanics
as a mechanism to share an unconditionally secure key between two parties. Since the first
protocol (BB84 or the four-state protocol) was proposed in the mid 1980s \citep{BB84},
the field has slowly grown; it now encompasses many different
protocols, using a variety of quantum processes to enable ever more secure
sharing of information. Still amongst the most widely
used, BB84 is one of the most straightforward; using two sets of two non-orthogonal basis states,
the key is encrypted in the state sent, and when the classical bit-sifting phase
takes place Alice (the sender) communicates to Bob (the receiver) the basis used for a selection
of the states sent. If the error is within the acceptable bounds, they can be sure that
their key is secure, and communicate the basis used for the rest of the states. In this
way, the unconditional security is achieved.

One major problem with BB84 is its reliance on a single photon source for true unconditional security.
Consider the ideal for Eve (eavesdropper); no restrictions are made on her technology or capability other
than the laws of physics. It is then clear that if the source used to send the key sends two or more quantum
states per bit, Eve can execute a Photon Number Splitting (PNS) attack; for every pulse of two or more photons,
she stores one state and lets the other state(s) continue on to Bob. Once Alice reads out the bases she used, Eve
will therefore have the complete key without the knowledge of the other participants; the security is lost. This
can be generalised to all prepare and measure protocols.

The area of study for this report focuses on the use of a recent protocol, SARG04, as a means to improve the
robustness against PNS attacks as compared to the standard prepare and measure protocols. It compares its efficacy
to BB84 and others, and discusses the impact of decoy states and other practical methods to increase security.

The objectives for the report are as follows: to give a brief history of QKD and its possible impact on current
society; to discuss the limitations of historical protocols in the real world; to give a detailed analysis of the
SARG04 protocol and its benefits over previous protocols; and finally to give a brief outline of real world improvements
and limitations, either through practical engineering or new techniques.

The search methodology used in this report involved first doing a broad search of academic articles, using google scholar and similar
tools, and then narrowing the scope through progressively more specific boolean search terms; then using papers already found to aid understanding
of the research area, and to provide other papers to study in the form of references.

\section{The BB84 and B92 prepare and measure protocols}

In this chapter, we give a description of two QKD protocols; BB84 and B92.
They both belong to the family of \textit{prepare and measure} protocols, and as
such rely on sending individual quantum states (qubits), rather than coding
via entangled pairs or other means.

\subsection{BB84}

The BB84 protocol was the first proposed QKD protocol, introduced at
an IEEE conference in India by \citet{BB84}, to little fanfare at the
time \citep{historyBrassard}; it would grow to become the most well known
and widely tested example of a QKD protocol. Today, it serves as
the benchmark against which all others are measured.

\subsubsection{The protocol}
In BB84, Alice uses a single photon source to transmit a set of states to Bob,
encoded in the polarization of the photons. Both Alice and Bob agree to align
their polarizers in either the vertical/horizontal ($+$) basis, or the
complementary basis of $\pm 45 \degree$  ($\times$). Alice then transmits a set of photons
down the quantum channel, randomly choosing one of the two bases for each
photon, whilst Bob measures in his choice of basis for each photon received.

\begin{center}
\begin{tabular}{c c c}
	$\ket{H}$  & codes for & $0_+$ \\
	$\ket{V}$  & codes for & $1_+$ \\
	$\ket{+45}$  & codes for & $0_\times$ \\
	$\ket{-45}$  & codes for & $1_\times$ \\
\end{tabular}
\end{center}

Both Alice and Bob now have a list of sent of received bits, each with a basis. The second
phase of the protocol is the classical sifting step: over the unsecured classical channel, they
first start by comparing which bases were used for each bit, and discarding the bits for which
they used different bases. For a list of size $N$ this step will on average reduce its size by half,
to $N/2$. Having matched the measurement basis, this list is referred to as the \textit{raw key} \citep{gisin2002}.

Alice and Bob now reveal a random sample of their raw key to one another, to compare for errors. By
comparing each bit publicly over the classical channel, they can estimate the error rate for
the quantum channel. If no errors are found, the raw key is already the secret key. If there are
errors, Alice and Bob must either correct for them or discard their key \citep{reviewScariani}. Both these actions can
take place over the classical channel; hence this step is called the \textit{classical post-processing}.
At the end of this phase, depending on how much information Eve could possess, Alice and Bob either share
a secret key, or they must discard the potentially compromised key.

\subsection{B92}
The B92 protocol, involving just 2 non-orthogonal states, is the
most minimalist QKD protocol in terms of encoding. Described by \citet{B92},
the B92 coding allows the receiver to learn whenever they get
the bit sent without further discussion from Alice.

\subsubsection{The protocol}
B92 can be carried out using the two bases used in BB84. Following on from the above description, Alice sends either
$\ket{H}$ or $\ket{+45}$, and Bob chooses to measure the incoming bit in either the ($\times$) or the ($+$)
basis. Both of these states code for 0 in BB84; if Bob measures the state that codes for 1 ($\ket{-45}$ or
$\ket{V}$ respectively) he can be certain that Alice transmitted her bit in the opposite basis. Hence, B92
allows the participants to restrict their transmissions in the sifting phase to whether or not Bob made
a conclusive measurement for each bit sent. After discarding all bits for which Bob cannot be certain, the raw
key they are left with is on average $N/4$ bits long, for an initial transmission of $N$ bits.

After a simple comparison of raw key length to the length of the initial string sent by Alice for the classical
post processing step, the participants either possess a secret key, or have been alerted to the possibility
of Eve's presence.

\subsection{Discussion}
The BB84 and B92 protocols are two of the most rigourously tested QKD protocols, with many published articles
on their relative strengths and weaknesses. Ultimate proofs exist for both; a well known one for BB84
by \citet{proofBB84}; and similarly, for B92 there is \citet{tamakiProofB92}. Both of these proofs rely on
conversion to EDP entanglement protocols; shortly after the first entanglement-based QKD protocol was
described by \citet{E91}, prepare-and-measure protocols were shown to have equivalent entanglement-based
versions by \citet{edpEquivProof}. It must be noted, however, that the above proofs are valid only
for perfect single photon sources.

Although sometimes easier to implement than the more popular BB84, it is more difficult to establish
unconditional security of B92, as it is much more sensitive to losses and noise in the
quantum channel. In the original paper, it is shown to be necessary
to rely on a strong reference pulse to guard against
losses and noise; again the security of this implementation has been proven
\citep{tamakiStrongRefProofB92}.

In an idealised world, where perfect single photon sources were available,
these protocols would provide complete security with no extensions required.
However, this is not the case for practical applications of QKD;
as discussed in the following chapter, BB84 and B92 are highly susceptible to
Eve's methods when real world limitations are present on the protocols.

\section{Limitations of QKD - Eavesdropping techniques}
In most literature on QKD, Eve is assumed, for the completeness of security proofs, to have no restrictions
on her eavesdropping, other than the fundamental limitations of quantum mechanics itself; namely, the
no-cloning theorem and the effects of measurement on a free particle. Briefly described here are two of the
most common eavesdropping techniques that are considered for BB84 and B92, followed by a more in-depth look
at classification of eavesdropping strategies and discussion of the relevant literature.

\subsection{Intecept-resend}
Potentially the most straightforward eavesdropping technique is the intercept-resend
strategy, which functions exactly the same for both BB84 and  B92.
Eve essentially takes the same actions as Bob; with her unrestricted capabilities, performs
a quantum nondemolition measurement on the incoming photons from Alice, measuring in either the $\times$
or the $+$ basis. If she has measured in the basis used by Alice, the photon continues on to Bob,
and Eve has obtained full information whilst introducing no errors to the signal. However, if she has measured
in the wrong basis, her result will be uncorrelated with Alice's; meanwhile, she will have sent along
a modified state, so even if Bob measures in the same basis as sent by Alice, half the time he will get the
wrong result. \citep{reviewScariani}


\subsection{Photon Number Splitting attack - PNS}
In real world applications of QKD, the photon source is never a true strong single photon emitter. Typically
a weak coherent pulse laser source is used. \citep{satellites}
These sources emit pulses of coherent states, often containing 2 or more photons.

This presents a problem for the security of BB84 and B92, as described below.

\subsubsection{BB84}
The security weakness in coherent pulses comes from Eve's ability to nondestructively determine the number of photons
in a pulse. The principle of the PNS attack is that Eve will block all single photon pulses, and for any pulse where
multiple photons are detected, Eve will store in quantum memory a subset of the pulse, while allowing the rest to continue
on to Bob (through an ideal quantum channel, to ensure his receipt of the photons). During the sifting
phase, Alice and Bob's communications over the public channel can be used by Eve to construct
a complete key from the stored states. The major benefit to Eve with this method is that it does not introduce an error in the
states received by Bob; in fact, the only risk of detection comes from the losses due to single photon pulses being blocked \citep{kronberg2009}.

As long as these losses do not reach a critical threshold (dependent on the length of the communication channel and the expected losses),
Eve's actions remain undetected, and the security of the protocol is compromised.


\subsubsection{B92}
Against B92, the PNS attack is even more straightforward. No quantum memory is required; all that is sufficient is that Eve performs
the same measurement as Bob, and blocks the message in the event of an inconclusive result \citep{kronberg2009}. In this way, the losses are attributed
to channel losses; as long as a critical threshold is not reached (as above), Eve will obtain full information of the key. Again, due to
the lack of error in the received states, Eve will remain entirely unnoticed.

\subsection{Classification of eavesdropping strategies and further discussion}
Strategies for eavesdropping on QKD protocols can be generally split into two main groups;
\textit{individual} and \textit{coherent}. Individual attacks involve
Eve probing each qubit individually as she recieves them, whereas for coherent attacks
she may process multiple qubits at a time, and measure them \textit{coherently}; for
instance, she can store them in quantum memory, and need not measure the qubits until
some later point \citep{gisin2002}. The two types have different consequences for generating
a truly secure key.

\subsubsection{Individual attacks}
Individual attacks impose a higher limitation on Eve, as she cannot wait for the participants to enact the sifting
phase before she takes her measurements - she must measure sequentially, as must Bob. Intercept-resend is classified as an individual attack.

In intercept-resend, after she has completed the process,
Eve is left with full information of half the bits in the full key ($I_E = 0.5$).
The measurement process introduces an error rate of 25\% (QBER $= Q = 0.25$)
into the key recieved by Bob. Using the assumptions given by \citet{csiszarAssump},
this means no secret key can be extracted. This is in fact true for \textit{all} protocols under an individual-type
attack \citep{reviewScariani}.

Even in the case where Eve does not eavesdrop on all photons in the key, and instead on just a fraction $p$,
then clearly $Q = p/4$ and

\begin{align}
I_E	= p/2 = 2Q
\end{align}

More errors in the received qubits can then be assumed in worst case to be an increase in Eve's information,
along with a corresponding decrease in Bob's information. When Eve's maximal information is compared with Bob's error
(given by his Shannon information), an inequality is recovered which describes the relative advantage of Bob or Eve.
The point at which this advantage shifts to Eve can be expressed as a specific error rate $Q_0$:

\begin{align}
	I(\alpha, \beta) = \mathrm{max} \left\{ I(\alpha, \epsilon) \right\}
	\quad
	\Leftrightarrow
	\quad
	Q = Q_0
	\approx 15\%
\end{align}

Hence a secure key can only be extracted if $Q \leq 15\%$. \citep{qber15proof, gisin2002, huttner1995}

\subsubsection{Coherent attacks}
\citet{gisin2002} succintly summarises the work of \citet{proofBB84} and others
on the subject of coherent attacks; using two theorems, the upper bound is found for the QBER
of a protocol expected to withstand coherent attack.

The first theorem originates from the field of classical
cryptography \citep{csiszarAssump}; if Alice, Bob and Eve
at some point perform measurements on their quantum systems
they will obtain classical random variables $\alpha$, $\beta$
and $\epsilon$, respectively, with $P(\alpha, \beta, \epsilon)$ as the
joint probability distribution. The the necessary and sufficient condition
for Alice and Bob to extract a secret key is

\begin{align}
	I(\alpha, \beta) \geq I(\alpha, \epsilon)
	\qquad
	\mathrm{or}
	\qquad
	I(\alpha, \beta) \geq I(\beta, \epsilon)
\end{align}

Where $I(\alpha, \beta) = H(\alpha) - H(\alpha | \beta)$ denotes the mutual information,
and $H$ is the Shannon entropy.

The second theorem expresses Heisenberg's uncertainty relation in terms of available information
\citep{hall1995}: it sets a bound on the sum of information about Alice's key available to Bob
and Eve.

Let E and B be two observables in an $N$-dimensional
Hilbert space. Let $\epsilon$, $\beta$, $\ket{\epsilon}$ and $\ket{\beta}$ be the corresponding
eigenvalues and eigenvectors, respectively, and
let $c = \mathrm{max}_{\epsilon, \beta}\left\{\abs{\Braket{\epsilon|\beta}}\right\}$. Then

\begin{align}
	I(\alpha, \epsilon) + I(\alpha, \beta) \leq 2\mathrm{log}_2(Nc)
\end{align}

Where again, $I(\alpha, \epsilon) = H(\alpha) - H(\alpha | \epsilon)$ and
$I(\alpha, \beta) = H(\alpha) - H(\alpha | \beta)$ are the entropy differences
corresponding to the probability distribution of the eigenvalues $\alpha$ prior
to and deduced from and measurement by Eve and Bob, respectively.

Theorem 1 means that to generate a secure key, Bob must have more information than
Eve about the bits generated by Alice. Theorem 2 is a mathematical description of the
fact that if Eve performs some measurement providing her with information, then because of
the perturbation, Bob's information is necessarily limited.

Using symmetry arguments, and denoting the number of qubits received in the
correct basis by Bob as $n$, theorem two implies

\begin{align}
	I(\alpha, \epsilon) + I(\alpha, \beta) \leq n
\end{align}

Which simply means that the sum of Eve and Bob's information per qubit is
less than or equal to 1; they cannot collectively receive more information
than Alice sends out. Combined with theorem one, this leads to the result that
a secret key is obtainable whenever $I(\alpha, \beta) \geq n/2$.
Finally using $I(\alpha, \beta) = n\left[1-Q\mathrm{log}_2(Q) - (1-Q)\mathrm{log}_2(1-Q)\right]$,
the bound for $Q$ (the QBER) can be obtained:
\begin{align}
	Q\mathrm{log}_2(Q) + (1-Q)\mathrm{log}_2(1-Q) \leq 1/2
	\qquad
	\Rightarrow
	\qquad
	Q \leq 11\%
\end{align}

This bound, when arrived at this way in particular, is only valid in the case where the key is much longer than number of
qubits Eve attacks coherently - allowing the Shannon information used to represent averages over
many measurements which return classical, random variables. However, the full proof given by
\citet{proofBB84} can still be used even in the event of Eve coherently attacking an unlimited number
of qubits. Precisely the same bound of $11\%$ QBER is recovered.

\subsubsection{Multi-photon pulses}
The two previous sections dealt with the classification of attacks Eve might perform on a protocol
that transmits a number of states, representing some string of symbols. In summary, if Eve can only be
expected to perform individual attacks, then the threshold of QBER before a sifted key becomes insecure
(assuming an infinite, or finite but large raw key) is $15\%$; if she has unlimited capacity to coherently measure
the states sent over the quantum channel, then the upper bound is $11\%$. But what if Alice transmits to Bob
not single quantum states, but instead pulses of multiple states? This is the reality for practical QKD \citep{huttner1995}.
Usually such weakly pulsed laser sources have low photon number $\mu$ per pulse; typically $\mu \approx 0.1$ \citep{reviewScariani}.

In this circumstance, Eve may perform the PNS attack described above; the effect on security can be quite large
indeed. Remember that Eve is not restricted in the technology she uses; while all currently known transmission
mediums incur some loss over distance, Eve could replace the channel between Alice and Bob by a perfect
lossless channel, and with the extra power gained she is free to discard a certain proportion of pulses. Typical
attenuation values for optical fibre are on the order of $10^{-2} \si{\dB \km^{-1}}$; most research findings indicate that
under such conditions security can only be guaranteed over a medium distance; between 50 and $200\si{\km}$, depending on experimental
parameters and assumptions \citep{perf2protocols, satellites, experimentalComparison}.

But how realistic is a quantum nondemolition measurement, or a lossless channel? In recent times,
quantum nondemolition measurements have increasingly been the subject of new research \citep{brassard2000};
ideal quantum nondemolition photon number measurements are beyond current technologies, although it may
be reasonable to assume that they are possible \citep{nogues1999}.

For Eve to count photon number for a pulse, she must measure it without disturbing the degree of
freedom encoding the qubit. Eve must then store the qubit, in either a lossless looped
channel, or by mapping the qubit to quantum memory. This may be unrealistic;
as noted above, there is no perfect physical medium
for transmission, even in theory, due to unavoidable Rayleigh scattering.
Attenuation of the qubits Eve has stored reduces her information, and Alice and Bob
may wait minutes before carrying out the sifting phase \citep{reviewScariani}; consequently, even if she chooses to
use the quantum memory, it must have close to unlimited decoherence time. Two possibilities left for Eve are suggested
by \citet{gisin2002}; either she must use high-fidelity, near lossless quantum teleportation of the qubits, or
she can convert the photons to another wavelength, again without disturbing the qubit. In the forseeable future,
neither option is realistic; however advances in quantum and optical technologies may make PNS attacks a serious threat.

%------------------------------------------------


%----------------------------------------------------------------------------------------
\bibliography{bibliography.bib}
\end{document}
